Titeln på avhandlingens språk

### 2022-09-06 model.tex
started verification

We use Python~\num{3.10} to implement two variants of the above described model.
The first of these samples execution times directly from the empirical data from~\cite{olguinmunoz:impact2021}; we will refer to it hereafter as the \emph{empirical model}.
The second corresponds to one which first fits a theoretical \ac{exGaussian} distribution to the data before sampling; we will refer to this one as the \emph{theoretical model}.
We also implement a reference model which uses a constant execution time of \SI{5.23}{\second}, which we in turn call the \emph{naive model}.
This value of \SI{5.23}{\second} corresponds to the mean execution time of steps with the lowest level of impairment and a transition tag of \emph{no transition}.
\todo[inline]{Transition fade distance was 4 instead of 8, need to mention?}

>>>>

We use Python~\num{3.10} to implement two variants of the above described model.
The first of these samples execution times directly from the empirical data from~\cite{olguinmunoz:impact2021}; we will refer to it hereafter as the \emph{empirical model}.
The second corresponds to one which first fits a theoretical \ac{exGaussian} distribution to the data before sampling; we will refer to this one as the \emph{theoretical model}.
We also implement a reference model which uses a constant execution time of \SI{5.23}{\second}, which we in turn call the \emph{naive model}.
This value corresponds to the mean execution time of steps with the lowest level of impairment and a transition tag of \emph{no transition}.
\todo[inline]{Transition fade distance was 4 instead of 8, need to mention?}

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figs/EdgeDroid2ExperimentalSetup.png}
    \caption{%
        Experimental setup we used to study the implications of the realistic models of human behavior for \ac{WCA}.
        We deploy containerized instances of the client-server loop running the models on a testbed consisting of \num{10} Raspberry Pi clients connected to a cloudlet over a \ac{COTS} \acs{IEEE} \num{802.11}n access point.
    }\label{fig:expsetup}
\end{figure}

These models are integrated into client software for communicating with an adapted and instrumented version of the Gabriel~\cite{Chen2015LEGO,Chen2018application} \ac{WCA} backend running variants of the LEGO task.
We use these client-server loops to illustrate the implications of the realistic timing models, which react to changes in system responsiveness in real-time, when compared to the static, naive model.
Up to \num{10} of these loops are deployed on the testbed shown in \cref{fig:expsetup}, consisting of \num{10} Raspberry Pi clients connected to a cloudlet over a \ac{COTS} \acs{IEEE} \num{802.11}n link.

\begin{figure}
    \centering
    \includegraphics[width=.8\columnwidth]{figs/numclients_vs_duration.png}
    \caption{}\label{fig:scaling_duration}
\end{figure}
